full title

### 2020-11-19 paper/pldi21/intro.tex
Updated intro.tex with the explanation of dynamic shortcut
Updated intro

In this paper, we propose a novel \textit{dynamic shortcut} technique to
leverage high performance of dynamic analysis for static analysis by freely
switching between them in a sound way.  Our key observation is that we can
use concrete semantics for specific program parts while preserving the soundness
if they are not dependent with meaning of abstract values.  For example, the
third line of the following program passes the abstract value \jscode{v} stored
in \jscode{obj.p1} to the variable \jscode{x}:
\begin{lstlisting}[style=myJSstyle,numbers=none]
var v = ... // an abstract value
var obj = { p1: v }, y = "p";
x = obj[y + 1];
\end{lstlisting}
Even though \jscode{obj} contains an abstract value \jscode{v}, the semantics of
the third line does not dependent with the meaning of \jscode{v}.  To utilize
this observation in dynamic shortcut, we introduce \textit{sealed symbolic
execution}, which is an augmented concrete execution with sealed symbolic
values.  We represent each abstract value as a sealed symbolic value, which is a
symbolic value that detects when trying to access its actual meaning.  To
evaluate our approach, we implemented $\tool$ by extending the existing
JavaScript static analyzer SAFE with dynamic shortcut.  For evaluation of
$\tool$, we analyzed abstracted versions of \inred{77} official tests of
\inred{Lodash 4} library.

>>>>

In this paper, we propose a novel \textit{dynamic shortcut} technique to
leverage high performance of dynamic analysis for static analysis by freely
switching between them in a sound way.  A dynamic shortcut consists of three
parts that 1) dumps the current abstract state to the corresponding sealed
symbolic state, 2) performs dynamic analysis on the sealed symbolic state, and
3) updates the abstract state with the result of dynamic analysis.  Our key
observation is that we can use concrete semantics for specific program parts
while preserving the soundness if they are not dependent with meaning of
abstract values.  For example, the third line of the following program passes
the abstract value \jscode{v} stored in \jscode{obj.p1} to the variable
\jscode{x}:
\begin{lstlisting}[style=myJSstyle,numbers=none]
var v = ... // an abstract value
var obj = { p1: v }, y = "p";
x = obj[y + 1];
\end{lstlisting}
Even though \jscode{obj} contains an abstract value \jscode{v}, the semantics of
the third line does not dependent with the meaning of \jscode{v}.  To utilize
this observation in dynamic shortcut, we introduce \textit{sealed symbolic
execution}, which is an augmented concrete execution with sealed symbolic
values.  We represent each abstract value as a sealed symbolic value, which is a
symbolic value that detects when trying to access its actual meaning.  To
evaluate our approach, we implemented $\tool$ by extending the existing
JavaScript static analyzer SAFE with dynamic shortcut.  For evaluation of
$\tool$, we analyzed abstracted versions of \inred{77} official tests of
\inred{Lodash 4} library.
